\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-04-01 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
make space for fire box
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64965 15284696-431f-4ddb-bdfa-cd5b030d7da7

\bigskip
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 0 0 125}, clip]{geomorphon}
Geomorphons for part of Yakima Training Center (area 5x3~km, USA)
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{geomorphon_tangible_high_tatras}
Ridges and valleys detected on the sand physical model of High Tatras (Slovakia) using \gamodule{r.geomorphon} integrated in Tangible Landscape system
\end{minipage}
}

>>>>

\bigskip
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 0 0 185}, clip]{geomorphon}
Geomorphons for part of Yakima Training Center (area 5x3~km, USA)
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 30 0 90}, clip]{geomorphon_tangible_high_tatras}
Ridges and valleys detected on the sand physical model of High Tatras (Slovakia) using \gamodule{r.geomorphon} integrated in Tangible Landscape system
\end{minipage}
}
